1 Report ASP20 Boost

### 2020-08-15 Reports/term_paper/TERM_PAPER.Rmd
- Term Paper - Base structe - Cover page.

---
title: "Report ASP20 Boost"
author:
- Johannes Strauß
- Levin Wiebelt
- Sebastian Aristizabal
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  pdf_document:
    keep_tex: no
    latex_engine: xelatex
    template: null
    toc: yes
    toc_depth: 2
documentclass: report
geometry: left=4cm, right=3cm, top=2.5cm, bottom=2.5cm
lof: FALSE
lot: FALSE
bibliography:
- citavi.bib
- packages.bib
subtitle: First Report
biblio-style: apalike
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

@@

In *part 2* of this report we explain the concept of boosting and elaborate on how it suites to address the problem of location-scale regression. 
In *part 3* we describe our implementation milestones, whereby *part 4* especially elaborates on componentwise boosting. 
In *part 5* we present our thoughts on upcoming challenges and critical aspects of the package development.

# 2. Concept: Boosting

@@

\begin{equation}
ll = \frac{1}{2\pi\exp(Z\Gamma)^2}\times\exp(-\frac{u^2}{2\exp(Z\Gamma)^2})
\end{equation}

# 3. Implementation

@@

# 4. Functionality: Componentwise Boosting

### 1. Beta

\begin{equation} 
\begin{aligned}
\beta_{j}^{(0)} = 0, \text{ for} j = 1,..,k. \\
u_i = y - X\hat{\beta}^{(t-1)} \\
\hat{b}_j = ((\vec{x}^j)^T \space\vec{x}^j)^{-1}((\vec{x}^j)^T \vec{u} \\
\end{aligned}
\end{equation}

### 2. Gamma

\begin{equation} 
\begin{aligned}
\gamma_{j}^{(0)} = 0, \text{ for} j = 1,..,k. \\
u_i = \text{deviance} \\
\hat{b}_j = U^2Z^2e^{-2(Z\Gamma)} \\
\end{aligned}
\end{equation}

### 3. Same procedure.

Fit separate models for all covariates i.e obtain

\begin{equation} 
\hat{b}_j = ((\vec{x}^j)^T \space\vec{x}^j)^{-1}((\vec{x}^j)^T \vec{u}, \text{ for} \space j = 1,..,k. 
\end{equation}

And determine the best fitting variable via

\begin{equation} 
j^* = \arg\min_{j = 0,..,k} \sum_{i=1}^{n}(u_i-x_{ij}\hat{b}_j)^2.
\end{equation}

\begin{equation} 
\begin{aligned}
\hat{\beta}_{j^*}^{(1)}  = \hat{\beta}_{j^*}^{(0)}+ \nu\hat{b}_{j^*} \\
\hat{\beta}_{j}^{(1)}  = \hat{\beta}_{j}^{(0)}, j\neq j^*.
\end{aligned}
\end{equation}

# 5. Prospects

## Further Functionalities

The most important functionality we intend to implement in our package is the optimization of the number of iterations via cross validation. 
To work out the theoretical concept behind this idea is, as well as to implementing it are our current next goals.
One further, rather loose, idea is to find ways to optimize the learning rate in our boosting algorithm.

## Stability

We intend to implement further automated unit tests. 
This will enable us to assess quickly the stability of our code given differing inputs.
We also intend to implement measures for proneness reduction to input errors.

## Performance

* A major performance problem in our code is that small learning rates for the $\beta$-booster lead to a  sharp increase of our code's processing time. This remains to be solved.
* A good choice of starting values for $\beta$ and $\gamma$ may enhance performance. A possible candidate is the mean of the response.

## Further Aspects

* Allow user-input of the LocationScaleRegressionBoost-model in form of a data frame, for example by allowing to pass an optional "data"-argument as known from the `lm-call`. This may reduce proneness to input-errors.

* Visualize the results of the boosted estimates

* Document the extension of the R6-Class properly and inherit documentation of the `LocationScaleRegression-Class` using roxygen2.

>>>>

---
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  pdf_document:
    keep_tex: no
    latex_engine: xelatex
    template: null
    toc: yes
    toc_depth: 2
    includes:
        in_header: preamble.tex
        before_body: frontpage.tex
documentclass: report
geometry: left=4cm, right=3cm, top=2.5cm, bottom=2.5cm
lof: FALSE
lot: FALSE
bibliography:
- citavi.bib
- packages.bib
biblio-style: apalike
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

@@

In *part 2*  
In *part 3*  
In *part 5*

# 2 Model and Methods

## Concept: Boosting

@@

\begin{equation}
ll = \frac{1}{2\pi\exp(Z\gamma)^2}\times\exp(-\frac{u^2}{2\exp(Z\gamma)^2})
\end{equation}

## Functionality: Componentwise Boosting

### 1. Initialize the regression coefficients

\begin{equation} 
\begin{aligned}
\beta_{j}^{(0)} = 0, \text{ for} j = 1,..,k. \\
\gamma_{j}^{(0)} = 0, \text{ for} j = 1,..,k. \\
\end{aligned}
\end{equation}

### 2. Compute the negative gradients

Beta
\begin{equation} 
\begin{aligned}
u_i = y - X\hat{\beta}^{(t-1)} \\
\hat{b}_j = ((\vec{x}^j)^T \space\vec{x}^j)^{-1}((\vec{x}^j)^T \vec{u} \\
\end{aligned}
\end{equation}

Gamma
\begin{equation} 
\begin{aligned}
u = y - X\hat{\beta}^{(t-1)} \\
u_i = X\hat{\beta}^{(t-1)}/Z\hat{\gamma}^{(t-1)} \\
\hat{b}_j = u^2(\vec{z}^j)^Te^{-2(Z\hat{\gamma}^{(t-1)})} \\
\end{aligned}
\end{equation}

### 3. Fit separate models for all covariates

Beta
\begin{equation} 
\hat{b}_j = ((\vec{x}^j)^T \space\vec{x}^j)^{-1}((\vec{x}^j)^T \vec{u}, \text{for} \space j = 1,..,k. 
\end{equation}

Gamma
\begin{equation} 
\hat{b}_j = ((\vec{z}^j)^T \space\vec{z}^j)^{-1}((\vec{z}^j)^T \vec{u}, \text{ for} \space j = 1,..,k. 
\end{equation}

And determine the best fitting variable via:

Beta
\begin{equation} 
\begin{aligned}
u_i = y-X\hat{\beta}^{(t-1)} \\
j^* = \arg\min_{j = 0,..,k} \sum_{i=1}^{n}(u_i-x_{ij}\hat{b}_j)^2\\
\end{aligned}
\end{equation}

Gamma
\begin{equation} 
\begin{aligned}
u_i = X\hat{\beta}^{(t-1)}/Z\hat{\gamma}^{(t-1)} \\
j^* = \arg\min_{j = 0,..,k} \sum_{i=1}^{n}(u_i-x_{ij}\hat{b}_j)^2
\end{aligned}
\end{equation}

Beta
\begin{equation} 
\begin{aligned}
\hat{\beta}_{j^*}^{(t)}  = \hat{\beta}_{j^*}^{(t-1)}+ \nu\hat{b}_{j^*} \\
\hat{\beta}_{j}^{(t)}  = \hat{\beta}_{j}^{(t-1)}, j\neq j^*.
\end{aligned}
\end{equation}

Gamma
\begin{equation} 
\begin{aligned}
\hat{\gamma}_{j^*}^{(t)}  = \hat{\gamma}_{j^*}^{(t-1)}+ \nu\hat{b}_{j^*} \\
\hat{\gamma}_{j}^{(t)}  = \hat{\gamma}_{j}^{(t-1)}, j\neq j^*.
\end{aligned}
\end{equation}

# 3. Software Implementation

@@

# 4. Simulation Studies

# 5. Discussion/Outlook.
